\documentclass[letterpaper,10pt,twoside,twocolumn,openany]{book}

\begin{document}
	
	% Your content goes here
	
	% Comment this out if you're using the article class.
	\chapter{Welcome to the Free Isles of Tashinori}
	
	\section{Introduction}
	
	The Free Isles of Toshinori is the name of the large archipelago that resides in the sapphire blue waters of the Antara Ocean. They became the Free Isles after an adventurer named Toshinori Zepar slayed the Hobgoblin king that controlled the vast majority of the islands. He led the conquest of the islands, but turned down being a king, giving the islands true freedom. 
	
	\section{About the Setting}
	
	The world that the Free Isles exists in is  relatively young one, only 1,100 years or so.  The overall flavor of the world is somewhere between Heroic Fantasy and Sword \& Sorcery.[DMG p38.] The world is full of extremes, both darkness and light.
	
	Standard Magic: Arcane magic is common throughout the lands, though some nations have stricter laws on its practice. Natural magic is used exclusively by Rangers (Druids are folklore) and Divine Magic is widely accepted because of its healing properties.
	
	Pantheon: I use a modified \href{https://stone-3.obsidianportal.com/wikis/the-dawn-war-pantheon}{Dawn War pantheon}. The major modification is the death of Pelor by the hand of Asmodeus; who struck him down on the Material plane back before the Greater Gods made a pact to not walk the Material. Sarenrae (Pathfinder deity) took Pelor’s place in his domain.	
	
\end{document}
